% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jim Liu}

\basicInfo{
  \email{hldh214@gmail.com} \textperiodcentered\ 
  \phone{(+86) 133-4292-4091} \textperiodcentered\ 
  \linkedin[realjimliu]{https://www.linkedin.com/in/realjimliu}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Wuhan University of Engineering Science (WUHUES)}, Wuhan, China}{2015 -- 2019}
\textit{B.S.} in Computer Science (CS)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Addnewer Inc.} Wuhan, China}{Jun. 2019 -- Present}
\role{Senior Software Engineer} {Full-time}
Brief introduction: Backend development, mainly using PHP programming language.
\begin{itemize}
  \item Implemented tgi calculate feature for Consumer-Insight-Analysis project.
  \item Optimized BI system with 15\% performance improvement.
  \item Upgraded old-school style and legacy code into newer code standard with zero accident.
\end{itemize}

\datedsubsection{\textbf{Buff2steam Projects}}{Jan. 2019 -- Present}
\role{Maintainer}{Individual Projects}
Brief introduction: A Steam trade bot with some fascinating features.
\begin{itemize}
  \item Multi source site supported.
  \item Custom goods type and price filter.
  \item Experimental auto-trade function with ASF embed.
\end{itemize}

\datedsubsection{\textbf{Recorder Projects}}{Aug. 2019 -- Present}
\role{Maintainer}{Individual Projects}
Brief introduction: A HLS recorder and uploader.
\begin{itemize}
  \item Easy to be further customized or extended.
  \item Full support for HLS streaming record based on  ffmpeg.
  \item Automatic upload after record finished.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: PHP == Python > Javascript > Java
  \item Platform: Linux
  \item Development: HTTP, SQL, Git, OOP, MVC
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \url{https://hldh214.github.io}
  \item GitHub: \url{https://github.com/hldh214}
  \item Stack Overflow: \url{https://stackoverflow.com/users/6266737/jim}
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

\end{document}
